---
title: ModÃfÂ©lisation des montants des sinistres et des frÃfÂ©quences des sinistres--
  Notebook
output:
  html_notebook: default
  html_document: default
---


#Read and prepare Data
#Histogramme
```{r}
SinistreData=read.csv("SinistreData.csv")
str(data)
table(SinistreData$montant)
table(SinistreData$nombres)
SinistreData$nombres[1]
SinistreData$montant[1]
plot(table(SinistreData$nombres))
plot(table(SinistreData$montant))
```


#Modelisation
```{r}
install.packages("fitdistrplus")
library(fitdistrplus)
```



                    # I. SinistreData$nombres
# (1)  fit of a poisson distribution
```{r}
fitp <- fitdist(SinistreData$nombres,"pois")
summary(fitp)

```
```{r}
plot(fitp)
```
```{r}
cdfcomp(fitp, addlegend=FALSE)

```
```{r}
ppcomp(fitp, addlegend=FALSE)

```
```{r}
qqcomp(fitp, addlegend=FALSE)

```



# (2) fit of a negative binomial distribution
```{r}
fitnb <- fitdist(SinistreData$nombres,"nbinom")
summary(fitnb)

```

```{r}
plot(fitnb)

```

```{r}
cdfcomp(fitnb, addlegend=FALSE)

```

```{r}
ppcomp(fitnb, addlegend=FALSE)

```

```{r}
qqcomp(fitnb, addlegend=FALSE)

```


# (3) fit of a  binomial distribution
```{r}
fitBi=fitdist(SinistreData$nombres, dist="binom", fix.arg=list(size=11), start=list(prob=0.3))
summary(fitBi)
```

```{r}
plot(fitBi)

```

```{r}
cdfcomp(fitBi, addlegend=FALSE)

```

```{r}
ppcomp(fitBi, addlegend=FALSE)

```

```{r}
qqcomp(fitBi, addlegend=FALSE)

```


# (4) Comparison of various fits #cumulative distribution function
```{r}

cdfcomp(list(fitp,fitnb,fitBi), legendtext=c("poisson", "negative binomial", " binomial"))
```
```{r}
gofstat(list(fitp,fitnb,fitBi))

```


                    # II. SinistreData$nombres
# (1) fit of a gamma distribution by maximum likelihood estimation
```{r}
fitg <- fitdist(SinistreData$montant, "gamma")
summary(fitg)
```
```{r}
cdfcomp(fitg, addlegend=FALSE)

```

```{r}
denscomp(fitg, addlegend=FALSE)

```

```{r}
ppcomp(fitg, addlegend=FALSE)

```

```{r}
qqcomp(fitg, addlegend=FALSE)

```



# (2) fit of a lognormal distribution by maximum likelihood estimation
```{r}
fitln <- fitdist(SinistreData$montant, "lnorm")
summary(fitln)
```
```{r}
plot(fitln, histo = FALSE, demp = TRUE)

```

```{r}
cdfcomp(fitln, addlegend=FALSE)

```

```{r}
denscomp(fitln, addlegend=FALSE)

```

```{r}
ppcomp(fitln, addlegend=FALSE)

```

```{r}
qqcomp(fitln, addlegend=FALSE)

```


# (3) fit of a weibull distribution by maximum likelihood estimation
```{r}
fitW <- fitdist(SinistreData$montant, "weibull")
summary(fitW)
```
```{r}
plot(fitW, histo = FALSE, demp = TRUE)

```

```{r}
cdfcomp(fitW, addlegend=FALSE)

```

```{r}
denscomp(fitW, addlegend=FALSE)

```

```{r}
ppcomp(fitW, addlegend=FALSE)

```

```{r}
qqcomp(fitW, addlegend=FALSE)

```



# (4) fit of a normal distribution by maximum likelihood estimation
```{r}
fitn <- fitdist(SinistreData$montant, "norm")
summary(fitn)
```
```{r}
plot(fitn, histo = FALSE, demp = TRUE)

```

```{r}
cdfcomp(fitn, addlegend=FALSE)

```

```{r}
denscomp(fitn, addlegend=FALSE)

```

```{r}
ppcomp(fitn, addlegend=FALSE)

```

```{r}
qqcomp(fitn, addlegend=FALSE)

```



# (5) Comparison of various fits
```{r}
cdfcomp(list(fitW, fitg, fitln, fitn), legendtext=c("Weibull", "gamma", "lognormal", "normal"))

```
```{r}
denscomp(list(fitW, fitg, fitln,fitn), legendtext=c("Weibull", "gamma", "lognormal", "normal"))
```

```{r}
qqcomp(list(fitW, fitg, fitln, fitn), legendtext=c("Weibull", "gamma", "lognormal", "normal"))
```

```{r}
ppcomp(list(fitW, fitg, fitln, fitn), legendtext=c("Weibull", "gamma", "lognormal", "normal"))
```

```{r}
gofstat(list(fitW, fitg, fitln, fitn), fitnames=c("Weibull", "gamma", "lognormal", "normal"))
```








